```{r}
library(tidyverse)
library(magrittr)
library(tidyr)
library(dplyr)
library(ggplot2)
```
https://www.kaggle.com/datasets/jillanisofttech/brain-stroke-dataset

```{r}
stroke2 = read.csv("BrainStroke2.csv")
stroke2
```
Now, I want to narrow down the columns to only the ones I am interested in`

```{r}
Bstroke <- stroke2 %>%
  select(Gender, age, hypertension, heart_disease, bmi, smoking_status)
Bstroke
```
Now, to analyze who is most/least prone to having a stroke
```{r}
brainstrokeA <- Bstroke %>%
                    filter(Bstroke$smoking_status == "smokes")
brainstrokeA
```

```{r}
brainstrokeAA <- Bstroke %>%
                    filter(Bstroke$smoking_status == "formerly smoked")
brainstrokeAA
```

```{r}
brainstrokeB <- Bstroke %>%
                    filter(Bstroke$smoking_status == "never smoked")
brainstrokeB
```
```{r}
bs <- Bstroke %>%
          filter(Bstroke$heart_disease == 1)
bs
```
```{r}
bss <- Bstroke %>%
          filter(Bstroke$hypertension == 1)
bss
```
Surprisingly, it seems that the majority of stroke patients actually don't smoke/never smoked. Even more so, the stroke patients who have a heart disease or hypertension are the minority, which is also surprising. 


```{r}
mean(Bstroke$age, na.rm = TRUE)
median(Bstroke$age, na.rm = TRUE)
which.min(Bstroke$age)
which.max(Bstroke$age)
```
The ages range from 49 to 82 with the median age being 71 and the average age being about 69. 

```{r}
mean(Bstroke$bmi, na.rm = TRUE)
median(Bstroke$bmi, na.rm = TRUE)
which.min(Bstroke$bmi)
which.max(Bstroke$bmi)
```
The bmi's range from 22.4 to 48.9 with the median bmi being 29 and the avergae bmi being about 30-31

Overall, it is surprising looking at the data of stroke patients and anaylzing who is most/least prone to having a stroke. Non smokers are the majority, and those with hypertension and heart disease are the minority. Also, the ages, along with the bmi's have a wide range. 